Do Economics Majors Make More Than Other Majors?

### 2024-02-11 outputs/Paper/paper.qmd
updates to graphs

```{r}
#| include: false
#| warning: false
#| message: false
library(tidyverse)
library(gt)
library(shiny)
library(ggplot2)
library(scales)
library(gridExtra)
```

@@

@@

```{r}
#| label: tbl-constructed data
#| fig-cap: Sample of Constructed data from Bleemer and Mehta
#| echo: false
load("/cloud/project/Inputs/Raw Data/ACS_Data_UCSCEcon_NAICS.Rda")
gt(head(acs))

@@

```{r}
#| label: tbl-cleaned data
#| fig-cap: Sample of Cleaned Data of UCSC Students
#| echo: false
#| warning: false
#| message: false

load("/cloud/project/outputs/Data/Majors_Income_Cleaned.Rda")
gt(head(cleaned_majors_data))

@@

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| label: fig-majors income
#| tbl-cap: Histogram of Business, Arts, Sciences, and Applied Sciences majors wage income
#| warning: false

#summary(business)

business_hist <-
  business |>
  ggplot(aes(x =INCWAGE)) +
  geom_histogram() +
  scale_x_continuous(labels = scales::comma) +
  xlim(0, 200000) +
  theme_minimal() +
  labs(title = "Wages of Business Majors", x = "Wage Income")

arts_hist <-
  arts |>
  ggplot(aes(x =INCWAGE)) +
  geom_histogram() +
  scale_x_continuous(labels = scales::comma) +
  xlim(0, 200000) +
  theme_minimal() +
  labs(title = "Wages of Arts Majors", x = "Wage Income")

science_hist <-
  sciences |>
  ggplot(aes(x =INCWAGE)) +
  geom_histogram() +
  scale_x_continuous(labels = scales::comma) +
  xlim(0, 200000) +
  theme_minimal() +
  labs(title = "Wages of Sciences Majors", x = "Wage Income")

applied_science_hist <-
  applied_science |>
  ggplot(aes(x =INCWAGE)) +
  geom_histogram() +
  scale_x_continuous(labels = scales::comma) +
  xlim(0, 200000) +
  theme_minimal() +
  labs(title = "Wages of Applied Science Majors", x = "Wage Income")

grid.arrange(arts_hist, business_hist, ncol=2)
grid.arrange(science_hist, applied_science_hist, ncol=2)

@@

```{r}

>>>>

```{r}
#| include: false
#| warning: false
#| message: false
library(tidyverse)
library(gt)
library(shiny)
library(ggplot2)
library(scales)
library(gridExtra)
library(psych)
library(ggpubr)
```

@@

Replication DOI: https://doi.org/10.48152/ssrp-m299-mq34

@@

@@

@tbl-cleaned-data
```{r, fig.width = 6, fig.height = 5}
#| label: tbl-cleaned-data
#| fig-cap: Sample of Cleaned Data of UCSC Students
#| echo: false
#| warning: false
#| message: false

load("/cloud/project/outputs/Data/Majors_Income_Cleaned.Rda")
cols_width(gt(head(cleaned_majors_data)), everything() ~ pct(15))

@@

Our results are summarized in (@tbl-majors-income-summary).

```{r}
#| echo: false
#| eval: true
#| label: tbl-majors-income-summary
#| tbl-cap: Summary Statistics of Business, Arts, Sciences, and Applied Sciences Majors Wage Income
#| warning: false

Business_Majors <- unclass(summary(business$INCWAGE))
Arts_Majors <- unclass(summary(arts$INCWAGE))
Science_Majors <- unclass(summary(sciences$INCWAGE))
Applied_Science_Majors <- unclass(summary(applied_science$INCWAGE))
summary_majors <- data.frame(Business_Majors, Arts_Majors, Science_Majors, Applied_Science_Majors, check.names = FALSE, stringsAsFactors = FALSE)
summary_majors
```

```{r, fig.width = 10, fig.height = 5}
#| echo: false
#| eval: true
#| label: fig-majors-income
#| fig-cap: Histogram of Business, Arts, Sciences, and Applied Sciences majors wage Income
#| warning: false

business_hist <-
  business |>
  ggplot(aes(x =INCWAGE)) +
  geom_histogram() +
  scale_x_continuous(labels = scales::comma) +
  xlim(0, 200000) +
  theme_minimal() +
  labs(title = "Business Majors", x = "Wage Income")

arts_hist <-
  arts |>
  ggplot(aes(x =INCWAGE)) +
  geom_histogram() +
  scale_x_continuous(labels = scales::comma) +
  xlim(0, 200000) +
  theme_minimal() +
  labs(title = "Arts Majors", x = "Wage Income")

science_hist <-
  sciences |>
  ggplot(aes(x =INCWAGE)) +
  geom_histogram() +
  scale_x_continuous(labels = scales::comma) +
  xlim(0, 200000) +
  theme_minimal() +
  labs(title = "Sciences Majors", x = "Wage Income")

applied_science_hist <-
  applied_science |>
  ggplot(aes(x =INCWAGE)) +
  geom_histogram() +
  scale_x_continuous(labels = scales::comma) +
  xlim(0, 200000) +
  theme_minimal() +
  labs(title = "Applied Science Majors", x = "Wage Income")

ggarrange(arts_hist, business_hist, science_hist, applied_science_hist, ncol=2, nrow = 2)

@@

```{r, fig.width = 10, fig.height = 5}
#| echo: false
#| eval: true
#| label: fig-majors-industries
#| fig-cap: Bar Graph of Preferred Industries for Business, Arts, Sciences, and Applied Sciences Majors
#| warning: false

business_ind <-
  business |>
  ggplot(aes(y = Industry)) +
  geom_bar() +
  theme_minimal() +
  xlim(0, 6000) +
  labs(title = "Business Majors",  x = "Total Students")

arts_ind <- 
  arts |>
  ggplot(aes(y = Industry)) +
  geom_bar() +
  theme_minimal() +
  xlim(0, 6000) +
  labs(title = "Arts Majors", x = "Total Students")

sciences_ind <-
  sciences |>
  ggplot(aes(y = Industry)) +
  geom_bar() +
  theme_minimal() +
  xlim(0, 6000) +
  labs(title = "Sciences Majors", x = "Total Students")

applied_science_ind <-
  applied_science |>
  ggplot(aes(y = Industry)) +
  geom_bar() +
  theme_minimal() +
  xlim(0, 6000) +
  labs(title = "Applied Science Majors", x = "Total Students")

ggarrange(arts_ind, business_ind, sciences_ind, applied_science_ind, ncol = 2, nrow = 2)
```

(@fig-majors-income)

```{r, fig.width = 10, fig.height = 3}
#| echo: false
#| eval: true
#| label: fig1-industries-high-income
#| labe2: fig1-industries-low-income
#| fig-cap: Bar Graph of Preferred Industries for Business, Arts, Sciences, and Applied Sciences Majors
#| warning: false

publ <- subset(cleaned_majors_data, Industry %in% "Public Administration")
fir <- subset(cleaned_majors_data, Industry %in% "FIRE")
cons <- subset(cleaned_majors_data, Industry %in% "Construction") 
whol <- subset(cleaned_majors_data, Industry %in% "Wholesale Trade")
util <- subset(cleaned_majors_data, Industry %in% "Utilities")

public_admin <-
  publ |>
  ggplot(aes(x =INCWAGE)) +
  geom_histogram() +
  scale_x_continuous(labels = scales::comma) +
  xlim(0, 200000) +
  theme_minimal() +
  labs(title = "Public Administration", x = "Wage Income")

fire <-
  fir |>
  ggplot(aes(x =INCWAGE)) +
  geom_histogram() +
  scale_x_continuous(labels = scales::comma) +
  xlim(0, 200000) +
  theme_minimal() +
  labs(title = "Finance Insurance Realestate", x = "Wage Income")

construct <-
  cons|>
  ggplot(aes(x =INCWAGE)) +
  geom_histogram() +
  scale_x_continuous(labels = scales::comma) +
  xlim(0, 200000) +
  theme_minimal() +
  labs(title = "Construction", x = "Wage Income")

wholesale_trd <-
  whol |>
  ggplot(aes(x =INCWAGE)) +
  geom_histogram() +
  scale_x_continuous(labels = scales::comma) +
  xlim(0, 200000) +
  theme_minimal() +
  labs(title = "Wholesale Trade", x = "Wage Income")

utilities <-
  util|>
  ggplot(aes(x =INCWAGE)) +
  geom_histogram() +
  scale_x_continuous(labels = scales::comma) +
  xlim(0, 200000) +
  theme_minimal() +
  labs(title = "Utilities", x = "Wage Income")

ggarrange(public_admin, fire, construct, ncol = 3)
ggarrange(wholesale_trd, utilities, ncol = 2)

```{r}
#| echo: false
#| eval: true
#| label: tbl-industry-income-summary
#| tbl-cap: Summary Statistics of Public Administration, FIRE, Construction, Wholesale Trade, and Utilities Wage Income
#| warning: false

#Summary Statistics
public_administration_industry <- unclass(summary(publ$INCWAGE))
fire_industry <- unclass(summary(fir$INCWAGE))
construction_industry <- unclass(summary(cons$INCWAGE))
wholesale_trade_industry <- unclass(summary(whol$INCWAGE))
utilities_industry <- unclass(summary(util$INCWAGE))
summary_industries <- data.frame(public_administration_industry, fire_industry, construction_industry, wholesale_trade_industry, utilities_industry,  check.names = FALSE, stringsAsFactors = FALSE)
summary_industries
```
